Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-23 Draft/Draft20181218.Rmd
.

>>>>

```{r}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
   rename(Toplam_2013 = "2013") %>%
   rename(Toplam_2014 = "2014") %>%
   rename(Toplam_2015 = "2015") %>%
   rename(Toplam_2016 = "2016") %>%
   rename(Toplam_2017 = "2017")

product_Cluster2 <- product_Cluster[,-1]
rownames(product_Cluster2) <- substr(product_Cluster$Product_Group_Name, start=1, stop=47)

#Scale the values

product_Cluster2 <- scale(product_Cluster2)
head(product_Cluster2)

# Create distance matrix
distance <- get_dist(product_Cluster2)
fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

#Determine optimal cluster with Elbow Method
set.seed(11)
fviz_nbclust(product_Cluster2, kmeans, method = "wss")

#Determine Optimal Cluster with Silhoutte Method
fviz_nbclust(product_Cluster2, kmeans, method = "silhouette")

#Determine Optimal Cluster with Gap Statistics Method
set.seed(12)
gap_stat <- clusGap(product_Cluster2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
fviz_gap_stat(gap_stat)

# Compute k-means with 4 clusters 
k2 <- kmeans(product_Cluster2, centers = 4, nstart = 25)
print (k2)
fviz_cluster(k2, data = product_Cluster2)

"cluster: A vector of integers (from 1:k) indicating the cluster to which each point is allocated.
centers: A matrix of cluster centers.
totss: The total sum of squares.
withinss: Vector of within-cluster sum of squares, one component per cluster.
tot.withinss: Total within-cluster sum of squares, i.e. sum(withinss).
betweenss: The between-cluster sum of squares, i.e. $totss-tot.withinss$.
size: The number of points in each cluster."
